A statistical analysis on factors that contributed/slowed down the spread of COVID-19

### 2020-10-28 Discussion/Presentation.tex
PUB

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{varwidth}
\usepackage{beamerthemesplit}

@@

@@

\frame{\titlepage}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\author{Marzio De Corato}
\usepackage{varwidth}
\usepackage{beamerthemesplit}

\hypersetup{
    pdftitle = {A statistical analysis on factors that contributed/slowed down the spread of COVID-19}, % <-- Missing in PDF
    pdfauthor = {Marzio De Corato},
    pdfsubject = {Marzio De Corato project the exam: Machine learning, statistical
learning, deep learning and artificial intelligence - Unsupervised Learning}
}

@@

\usebackgroundtemplate{\includegraphics[width=\paperwidth]{Pic/coronavius-cases-worldwide-data}}

\author{}
\date{}

@@

\frame{\vspace{-2.5cm}\titlepage}

\usebackgroundtemplate{ }
